Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-09 paper-2023-acsos-pulverization.tex
write some intro

@@

>>>>

\newcommand{\ourframework}{Porbione}

@@

Recent research trends in topics related to the Internet of Things promote the idea of a cloud-edge continuum~\cite{DBLP:journals/iot/BittencourtISFM18},
an infrastructure composed of heterogeneous devices ranging from large and powerful cloud servers to small connected things
on which software computes in a distributed fashion,
optimising for performance and resource utilisation.
%
Exploiting this intriguing infrastructure, however, poses new challenges to the application designer.
%
Commonly, in fact, applications are designed with a specific infrastructure in mind,
whose assumptions leak into the application logic.

Previous work suggests a technique for decoupling business logic and deployment concerns
called \emph{pulverization}~\cite{FI2020-pulverization}.
%
In short, the core idea is to consider devices as \emph{logical} entities,
whose software can be designed as (or broken down to, if already existing) an ensemble of five micro-components
(behaviour, state, communication, sensors, and actuators)
whose actual host can be decided at deployment time.
%
This way, the designer can focus on the business logic at hand,
delaying an optimised deployment to later stages of the sofware design,
thus gaining resilience to changing infrastructures or non-functional requirements.
%
One limitation of the current pulverisation approach regards dynamicity:
although the application can be deployed on arbitrary systems,
there is no support for the reconfiguration of components in face of changing conditions or requirements.

In this work,
we continue the research on pulverised systems by providing two key contributions:
first, we extend the theoretical framework of pulverisation by adding support for
\emph{runtime configuration rules}, allowing pulverised components to move at runtime across different hosts;
the providing a practical implementation called \ourframework{} which,
to the best of our knowledge,
is the first \emph{practical framework supporting pulverisation} for a general-purpose language.
%
We exercise \ourframework{} with two case studies:
a small-scale real-wold demonstration, and a city-scale simulated scenario.
